---
output: html_document
---
### Course Project of Practical Machine learning

In this study, 6 participants were asked to perform barbell lifts correctly and incorrectly in 5 different ways. The goal is to use data collected from accelerometers on the belt, forearm, arm, and dumbell of the 6 participants to predict their manner of activity

#### Data loading, preprocessing and exploratory analysis   
First, we loaded the training data and remove the column with mostly NAs.   
```{r}
library(caret)
test<-read.csv("pml-testing1.csv",na.strings=c("NA",""))
training<-test[21:19642,]
test<-test[1:20,]
mostly_data<-apply(!is.na(training),2,sum)>19621
training<-training[,mostly_data]
test<-test[,mostly_data]
dim(training)
summary(training)
```   
We can see that the training dataset contains 19622 observations. After removing the columns with mostly NAs, there are 60 varaibles, including classe, the one to be predicted, which contains 5 classes.   
#### Fit prediction models using different ways and calcualte the 5-fold cross validation error.   
Different methods were used to build the prediction model and 5 fold cross validation errors were calculated. Random forest and naive bayes's method were not run because the memory of the computer is not enough.   
```{r}
### Prediction tree
modFit_rpart<-train(classe~.-X,data=training,method="rpart",trControl=trainControl(method="cv",number=5))
modFit_rpart$results
### LDA
modFit_lda<-train(classe~.-X,data=training,method="lda",trControl=trainControl(method="cv",number=5))
modFit_lda$results
### Random Forest
library(randomForest)
modFit_rf<- randomForest(classe~.-X, data=training)
modFit_rf
```   
From above, the accuracy of the three methods are 0.46, 0.85 and 0.99. So the error rate is 0.54 for predictive tree, 0.15 for LDA and 0.01 for Random forest.   
#### Apply random forest to test data  
We see that random forest gives the best cross validation error, so we apply this method to the test dataset
```{r}
predict(modFit_rf, test)
```   
The predicted classes are: B  A  B  A  A  E  D  B  A  A  B  C  B  A  E  E  A  B  B  B  
The expected error rate should be similar 0.01
